%%
%% ACKNOWLEDGMENTS
%%
\chapter*{Acknowledgments}
\label{acknowledgements}
{\footnotesize
My Master’s thesis has been carried out being a part of the Parsimonious Modelling(PM) group in Helsinki Institute for Information Technology (HIIT), Department of Information and Computer Science(ICS) in the Aalto University School of Science and Technology(TKK). First of all, I would like to thank my instructor DSc.(Tech.) Jaakko Hollm{\'e}n for his enthusiastic engagement in my research and his never ending stream of advice, ideas and support ranging from the minute technical details to the overall research ideas. A share of thanks also goes to the supervisor Prof. Samuel Kaski who invested his precious time in paper work and glancing manuscript. A big share of thanks also goes to the members of the PM group and the whole ICS, AIRC(Adaptive Informatics Research Center) laboratory and ALGODAN (Finnish Center of Excellence for Algorithmic Data Analysis Research) for providing splendid working and research environment.

I would also like to thank each and every professors, teachers and assistants involved in teaching and organizing MACADAMIA programme \cite{macadamia}. Initially, it was difficult but overall it has been a great learning experience. I would especially like to mention the names of Kai Puolam\"aki and Gemma C Garriga for their advice and suggestions during early part of MSc Degree studies. A big share of thanks also goes to my MACADAMIA mates Yao, Peter, Joel, Agha and Jing, the seniors especially Luis and Du\^san and the juniors especially Kranthi and Mudassar.

I would also like to thank my mates, the seniors Aditya and Sandeep as well as Gautam, Tashi, Marko, Tuomas, Timo, Ashis Ji. I would also like to thank other guys in Terassi for making the place a lively place to live in. If it weren’t for you guys, I might have graduated earlier but without you, I would never have  graduated. Yao and Saurav should have the credit for proof-reading my thesis and helping me with the English grammar and spelling. All the remaining errors are to be blamed on me for the last minute changes. Last but not the least my gratitude and thanks goes to my parents, family and relatives for their everlasting love and support.}

\parindent 0em
\begin{flushright}
\vskip0.5cm
Espoo, November 29, 2010

Prem Raj Adhikari
\end{flushright}

\clearpage
\thispagestyle{empty}


\vspace{8cm}

\begin{fquote}[{Anthony J. D'Angelo}] {\large  Wherever you go, no matter what the weather, always bring your own sunshine.}  \fqsource{{\large The College Blue Book}} \end{fquote} 
